Crossing Origins by Crossing Formats

### 2012-12-03 main.tex
typos

The current best-practice recommendation from Google~\cite{Google:ContentHosting} 
on hosting user-supplied content, is to serve the content from an origin that is 
completely separate, and isolated from the sensitive services. It also describes how 
Google moved away from sanitizing content , as it was found to be insufficient in 
many cases.

@@

Barth et al.~\cite{Barth+:SP09} focus on security implications of
content sniffing by browsers. They present content-sniffing XSS
attacks by crossbreeding HTML with other formats like postscript. They
show attacks on real systems like HotCRP, where an uploaded conference
paper in the postscript format is interpreted as malicious HTML by the
browser. They also propose a content-sniffing algorithm that does not
suffer that helps defending against these class of attacks while
maintaining compatibility.

@@

Wolf's OMG WTF PDF presentation~\cite{Wolf:CCC10} is one of the main
starting points for this work. The presentation explores the liberty
of the PDF format. In addition, it highlights that PDF interpreters
often disregard the specification demands. This particularly
relevant as it allows crossbreeding PDF with such
formats as ZIP and EXE.

>>>>

The current best-practice recommendation from Google~\cite{Google:ContentHosting} 
on hosting user-supplied content, is to serve the content from an origin that is 
completely separate, and isolated from the sensitive services. It also describes how 
Google moved away from sanitizing content, as it was found to be insufficient in 
many cases.

@@

Barth et al.~\cite{Barth+:SP09} focus on security implications of
content sniffing by browsers. They present content-sniffing XSS
attacks by crossbreeding HTML with other formats like PostScript. They
show attacks on real systems like HotCRP, where an uploaded conference
paper in the PostScript format is interpreted as malicious HTML by the
browser. They also propose a content-sniffing algorithm that does not
suffer that helps defending against these class of attacks while
maintaining compatibility.

@@

Wolf's OMG WTF PDF presentation~\cite{Wolf:CCC10} is one of the 
inspirations for our work. The presentation explores the liberty
of the PDF format. In addition, it highlights that PDF interpreters
often disregard the specification demands. This particularly
relevant as it allows crossbreeding PDF with such
formats as ZIP and EXE.
